---
title: "Extract & clean - Tesla (TSLA)"
author: "Yelko Bejarano"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(data.table)
library(dplyr)
library(lubridate)
library(ggplot2)
library(quantmod)

TICKER <- "TSLA"
KEYWORDS <- "\\b(TSLA|Tesla|Elon Musk|Model 3|Model Y|Model S|Model X|Cybertruck|Autopilot|Full Self-Driving|FSD|Gigafactory)\\b"
```

# 1. Load and filter

## 1.1. Check the ticker is in the news dataset

```{r}
unique_symbols <- unique(fread("../../nasdaq_exteral_data.csv", select = "Stock_symbol")$Stock_symbol)
TICKER %in% unique_symbols
```

## 1.2. Load news for the ticker (FNSPID)

```{r}
news_data <- fread(
  "../../nasdaq_exteral_data.csv",
  select = c("Date", "Article_title", "Stock_symbol", "Lsa_summary")
)
news_data <- news_data[Stock_symbol == TICKER]
news_data <- news_data[as.POSIXct(Date, tz = "UTC") >= as.POSIXct("2022-01-01", tz = "UTC")]

cat("News for", TICKER, ":", nrow(news_data), "\n")
```

## 1.3. Load Reddit comments (2022-2023) and filter by company keywords

```{r}
comments_2022 <- read_csv(
  "../../extraccion_reddit_v.1.1/wallstreetbets_Discussion_Threads_2022-01-01_to_2022-12-31_comments.csv",
  col_select = c(comment_id, body, score, comment_datetime_full),
  show_col_types = FALSE
)
comments_2023 <- read_csv(
  "../../extraccion_reddit_v.1.1/wallstreetbets_Discussion_Threads_2023-01-01_to_2023-12-31_comments.csv",
  col_select = c(comment_id, body, score, comment_datetime_full),
  show_col_types = FALSE
)

comments_raw <- bind_rows(comments_2022, comments_2023) %>%
  filter(grepl(KEYWORDS, body, ignore.case = TRUE, perl = TRUE))

cat("Raw comments for", TICKER, ":", nrow(comments_raw), "\n")
```

# 2. Time adjustments and filters

## 2.1. UTC -> EST

```{r}
comments_processed <- comments_raw %>%
  mutate(
    comment_datetime_est = with_tz(comment_datetime_full, tzone = "America/New_York"),
    comment_date_est = as.Date(comment_datetime_est),
    comment_hour = hour(comment_datetime_est),
    weekday_original = wday(comment_date_est)
  )

cat("Comments before temporal filters:", nrow(comments_processed), "\n")
```

## 2.2. Drop weekend comments

```{r}
# Drop full Saturday + Sunday (EST); Friday after-hours is moved to Monday below
comments_weekdays_only <- comments_processed %>%
  filter(!(weekday_original == 7 | weekday_original == 1))

cat("Weekend comments dropped:", nrow(comments_processed) - nrow(comments_weekdays_only), "\n")
cat("Remaining:", nrow(comments_weekdays_only), "\n")
```

## 2.3. After-hours -> next trading day

```{r}
comments_clean <- comments_weekdays_only %>%
  mutate(
    # After-hours (>= 16:00) -> next trading day (Fri -> Mon; Mon-Thu -> next day)
    trading_date = case_when(
      weekday_original == 6 & comment_hour >= 16 ~ comment_date_est + 3,
      weekday_original %in% 2:5 & comment_hour >= 16 ~ comment_date_est + 1,
      TRUE ~ comment_date_est
    )
  ) %>%
  select(-weekday_original)

cat("After-hours comments reassigned:", sum(comments_clean$comment_hour >= 16), "\n")
```

# 3. Validation and statistics

## 3.1. Weekend-removal validation

```{r}
weekday_distribution <- comments_clean %>%
  mutate(wd = wday(as.Date(comment_datetime_est), label = TRUE)) %>%
  count(wd) %>%
  mutate(pct = n / sum(n) * 100)

print(weekday_distribution)

has_weekend <- any(weekday_distribution$wd %in% c("sáb", "dom", "Sat", "Sun"))
if (has_weekend) {
  stop("Validation failed: weekend comments detected")
}
cat("\nValidation OK: no weekend comments\n")
```

## 3.2. Final descriptive statistics

```{r}
cat("Date range:", as.character(range(comments_clean$trading_date)), "\n")
cat("Total comments:", nrow(comments_clean), "\n")
cat("Comments with score > 0:", sum(comments_clean$score > 0, na.rm = TRUE), "\n")
cat("Comments with score < 0:", sum(comments_clean$score < 0, na.rm = TRUE), "\n")
cat("Mean score:", round(mean(comments_clean$score, na.rm = TRUE), 2), "\n")
```

## 3.3. Temporal distribution plot

```{r}
comments_clean %>%
  mutate(
    weekday = wday(as.Date(comment_datetime_est), label = FALSE),
    day = factor(weekday, levels = 2:6, labels = c("Mon", "Tue", "Wed", "Thu", "Fri"))
  ) %>%
  count(day) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ggplot(aes(x = day, y = pct)) +
  geom_col(fill = "#3498db", alpha = 0.8) +
  geom_text(aes(label = paste0(round(pct, 1), "%")), vjust = -0.5, size = 4) +
  labs(
    title = paste("Temporal distribution - comments", TICKER),
    subtitle = "Weekdays (Mon-Fri) | Sat-Sun removed | Fri after-hours -> Mon",
    x = NULL,
    y = "% comments"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", size = 14))
```

# 4. Deduplicate

```{r}
cat("Before dedup:", nrow(comments_clean), "\n")

comments_unique <- comments_clean %>%
  distinct(body, score, trading_date, .keep_all = TRUE)

cat("After dedup:", nrow(comments_unique), "\n")
cat("Duplicates removed:", nrow(comments_clean) - nrow(comments_unique), "\n")
```

# 5. Export

## 5.1. Write clean comments and news CSVs

```{r}
write_csv(comments_unique, paste0("comments_", tolower(TICKER), "_clean.csv"))
write.csv(news_data, paste0("news_", TICKER, ".csv"), row.names = FALSE)

cat("Exported: comments_", tolower(TICKER), "_clean.csv (", nrow(comments_unique), " rows)\n", sep = "")
```

## 5.2. Save prices and objects (RData)

```{r}
price <- getSymbols(TICKER, from = "2022-01-01", to = "2024-12-31", auto.assign = FALSE)
save(news_data, price, comments_unique, file = paste0(tolower(TICKER), "_data.RData"))

cat("Saved", paste0(tolower(TICKER), "_data.RData"), "\n")
```
