---
title: "Multi-company news analysis: news-sentiment tables"
author: "Yelko Bejarano"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: cosmo
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{array}
  - \usepackage{colortbl}
  - \usepackage{xcolor}
  - \usepackage{threeparttable}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 8
)

is_latex <- knitr::is_latex_output()
```

# =============================================================================
# PART A: CONFIGURATION
# =============================================================================

```{r config_principal}
# Methodological decisions (news, non-pooled; parallel to the comments analysis):
#
#   MANDATORY LAG: every news item -> NEXT trading day.
#     Publication times are unreliable, so to avoid data leakage any news dated t
#     affects t+1. For the same reason there is no AH/PM split for news (no M2).
#
#   MODELS:
#     Model A: net shift (ΔS)          -> parallel to M1 of comments
#     Model B: ΔS+ + ΔS- (pos/neg)     -> parallel to M3 of comments
#
#   STRATEGIES:
#     S1 = title-only      (sentiment of the title only)
#     S2 = smart-weighted  (title + summary, 30/70 weighting)

TICKERS <- c("AAPL", "AMD", "AMZN", "DIS", "GOOGL", "META", "MSFT", "NVDA", "TSLA")
# NFLX excluded: the master news dataset has no Netflix articles for 2022-2023.
# META is kept but has no news in the period, so it is skipped by the file guard.

ALGO_PRINCIPAL <- "roberta_stocks"
ESTRATEGIAS    <- c("S1", "S2")   # both are estimated and reported

ALGORITMOS_TODOS <- c(
  "finbert", "roberta_social", "roberta_stocks",
  "distilroberta_fin", "bert_sentiment"
)

MA_DIAS <- 7

DIR_BASE   <- getwd()
DIR_OUTPUT <- file.path(DIR_BASE, "RESULTADOS_NEWS_v1.0")
if (!dir.exists(DIR_OUTPUT)) dir.create(DIR_OUTPUT, recursive = TRUE)

ALGO_LABELS <- c(
  "finbert"           = "FinBERT",
  "roberta_social"    = "RoBERTa-Soc",
  "roberta_stocks"    = "RoBERTa-Stk",
  "distilroberta_fin" = "DistilRoB",
  "bert_sentiment"    = "BERT"
)

ESTRAT_LABELS <- c(
  "S1" = "Title-only",
  "S2" = "Smart-weighted"
)

# Binary algorithms (positive/negative, no neutral) -> shift_pos and shift_neg
# are linearly dependent (sum to 0): OLS drops one for collinearity.
ALGORITMOS_BINARIOS <- c("roberta_stocks")

cat("===================================================================\n")
cat("                CONFIGURATION NEWS\n")
cat(sprintf("  Companies:       %s\n", paste(TICKERS, collapse = ", ")))
cat(sprintf("  Primary algo:    %s (%s)\n",
            ALGO_PRINCIPAL, ALGO_LABELS[ALGO_PRINCIPAL]))
cat(sprintf("  Strategies:      %s\n", paste(ESTRATEGIAS, collapse = ", ")))
cat(sprintf("  MA control:      MA(%d)\n", MA_DIAS))
cat("===================================================================\n")
```

```{r librerias}
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(quantmod)
  library(zoo)
  library(sandwich)
  library(lmtest)
  library(knitr)
  library(kableExtra)
})
```

# =============================================================================
# PART B: HELPER FUNCTIONS
# =============================================================================

```{r funciones_estimacion}
# Estimate OLS with Newey-West HAC standard errors.
# Variables dropped by collinearity are emitted with Coef = NA so tables show
# "—" instead of an empty cell.
estimar_modelo <- function(formula_str, data, nombre_modelo, ticker, algoritmo,
                           estrategia) {
  formula_str <- gsub("\\s+", " ", formula_str)
  formula_modelo <- as.formula(formula_str)
  vars_en_formula <- all.vars(formula_modelo)

  vars_faltantes <- setdiff(vars_en_formula, names(data))
  if (length(vars_faltantes) > 0) {
    cat("      [!]", nombre_modelo, "-> MISSING VARS:",
        paste(vars_faltantes, collapse = ", "), "\n")
    return(NULL)
  }

  data_est <- data %>% select(all_of(vars_en_formula)) %>% na.omit()
  if (nrow(data_est) < 30) {
    cat("      [!]", nombre_modelo, "-> only", nrow(data_est), "obs (min 30)\n")
    return(NULL)
  }

  modelo_ols  <- lm(formula_modelo, data = data_est)
  robust_se   <- NeweyWest(modelo_ols, prewhite = FALSE, adjust = TRUE)
  coef_robust <- coeftest(modelo_ols, vcov = robust_se)

  n_obs    <- nrow(data_est)
  k_params <- length(coef(modelo_ols))
  r2_adj   <- summary(modelo_ols)$adj.r.squared
  aic_val  <- AIC(modelo_ols)
  aicc_val <- aic_val + (2 * k_params^2 + 2 * k_params) / (n_obs - k_params - 1)
  bic_val  <- BIC(modelo_ols)

  resultados <- data.frame()
  for (i in 1:nrow(coef_robust)) {
    var_name <- rownames(coef_robust)[i]
    p_val    <- coef_robust[i, "Pr(>|t|)"]
    sig_symbol <- ifelse(p_val < 0.001, "***",
                  ifelse(p_val < 0.01,  "**",
                  ifelse(p_val < 0.05,  "*",
                  ifelse(p_val < 0.1,   "$\\dagger$", ""))))

    resultados <- rbind(resultados, data.frame(
      Modelo     = nombre_modelo,
      Empresa    = ticker,
      Algoritmo  = algoritmo,
      Estrategia = estrategia,
      N          = n_obs,
      Variable   = var_name,
      Coef       = coef_robust[i, "Estimate"],
      Std_Error  = coef_robust[i, "Std. Error"],
      t_value    = coef_robust[i, "t value"],
      P_value    = p_val,
      Signif     = sig_symbol,
      AICc       = aicc_val,
      BIC        = bic_val,
      R2_adj     = r2_adj,
      stringsAsFactors = FALSE
    ))
  }

  # Variables dropped by collinearity: NA in coef(lm) and absent from
  # coeftest(). Emitted with Coef = NA so get_celda shows "—".
  coefs_lm <- coef(modelo_ols)
  vars_descartadas <- names(coefs_lm)[is.na(coefs_lm)]
  for (var_name in vars_descartadas) {
    resultados <- rbind(resultados, data.frame(
      Modelo     = nombre_modelo,
      Empresa    = ticker,
      Algoritmo  = algoritmo,
      Estrategia = estrategia,
      N          = n_obs,
      Variable   = var_name,
      Coef       = NA_real_,
      Std_Error  = NA_real_,
      t_value    = NA_real_,
      P_value    = NA_real_,
      Signif     = "",
      AICc       = aicc_val,
      BIC        = bic_val,
      R2_adj     = r2_adj,
      stringsAsFactors = FALSE
    ))
  }

  return(resultados)
}

# Format a table cell = coefficient + stars. NA -> "—" (dropped by collinearity)
fmt_celda <- function(coef, pval, digits = 4) {
  if (is.na(coef)) return("—")
  if (is.na(pval)) return(formatC(coef, format = "f", digits = digits))
  stars <- ifelse(pval < 0.001, "***",
           ifelse(pval < 0.01,  "**",
           ifelse(pval < 0.05,  "*",
           ifelse(pval < 0.1,   "$\\dagger$", ""))))
  coef_str <- formatC(coef, format = "f", digits = digits)
  paste0(coef_str, stars)
}

# Display name for a variable (without the algorithm or s1_/s2_ prefix)
nombre_var_display <- function(var_raw, algoritmo = NULL) {
  v <- var_raw
  if (!is.null(algoritmo)) v <- gsub(paste0("^", algoritmo, "_"), "", v)
  v <- gsub("^s[12]_", "", v)

  if (knitr::is_latex_output()) {
    lookup <- c(
      "(Intercept)" = "Intercept",
      "DJI_RET"     = "DJI RET",
      "DJI_VOL"     = "DJI VOL",
      "DJI_VOLUME"  = "DJI VOLUME",
      "NWK"         = "NWK",
      "ln_noticias" = "ln(news)",
      "shift"       = "$\\Delta S$ news",
      "shift_pos"   = "$\\Delta S^{+}$ news",
      "shift_neg"   = "$\\Delta S^{-}$ news"
    )
  } else {
    lookup <- c(
      "(Intercept)" = "Intercept",
      "DJI_RET"     = "DJI RET",
      "DJI_VOL"     = "DJI VOL",
      "DJI_VOLUME"  = "DJI VOLUME",
      "NWK"         = "NWK",
      "ln_noticias" = "ln(news)",
      "shift"       = "$\\Delta$S news",
      "shift_pos"   = "$\\Delta$S$^{+}$ news",
      "shift_neg"   = "$\\Delta$S$^{-}$ news"
    )
  }

  if (v %in% names(lookup)) return(lookup[v])
  if (grepl("^VOL_MA",    v)) return(paste0("VOL MA(",  MA_DIAS, ")"))
  if (grepl("^VOLUME_MA", v)) return(paste0("VOL. MA(", MA_DIAS, ")"))
  return(v)
}

cat("Helper functions defined\n")
```

# =============================================================================
# PART C: MAIN LOOP - PER-COMPANY PROCESSING (non-pooled)
# =============================================================================

```{r bucle_empresas, results='hide'}
RESULTADOS_ALL <- data.frame()
dji_df_global  <- NULL

cat("===================================================================\n")
cat("              NEWS PROCESSING (non-pooled)\n")
cat("===================================================================\n\n")

for (TICKER in TICKERS) {

  cat("\n===", TICKER, "===\n")

  # C.1 Load the S1 and S2 CSVs
  file_s1 <- file.path(DIR_BASE, TICKER,
    paste0("news_", tolower(TICKER), "_sentiments_S1_title_only.csv"))
  file_s2 <- file.path(DIR_BASE, TICKER,
    paste0("news_", tolower(TICKER), "_sentiments_S2_smart_weighted.csv"))

  if (!file.exists(file_s1) || !file.exists(file_s2)) {
    cat("  FILES NOT FOUND for", TICKER, "-> skipped\n")
    next
  }

  news_s1 <- suppressWarnings(read_csv(file_s1, show_col_types = FALSE))
  news_s2 <- suppressWarnings(read_csv(file_s2, show_col_types = FALSE))
  cat("  S1:", nrow(news_s1), "news | S2:", nrow(news_s2), "news\n")

  # C.2 MANDATORY LAG: every news item -> NEXT trading day
  procesar_fecha_lag <- function(df) {
    df %>%
      mutate(
        datetime_utc = ymd_hms(Date, tz = "UTC"),
        datetime_est = with_tz(datetime_utc, tzone = "America/New_York"),
        fecha_est    = as.Date(datetime_est),
        next_day     = fecha_est + 1,
        dow          = wday(next_day),
        trading_day  = case_when(
          dow == 7 ~ next_day + 2,   # Saturday -> Monday
          dow == 1 ~ next_day + 1,   # Sunday -> Monday
          TRUE     ~ next_day
        )
      ) %>%
      select(-next_day, -dow)
  }

  news_s1 <- procesar_fecha_lag(news_s1)
  news_s2 <- procesar_fecha_lag(news_s2)

  # C.3 Market data
  fecha_min <- min(c(news_s1$trading_day, news_s2$trading_day), na.rm = TRUE)
  fecha_max <- max(c(news_s1$trading_day, news_s2$trading_day), na.rm = TRUE)

  precio_accion <- tryCatch(
    getSymbols(TICKER, from = fecha_min - 30, to = fecha_max + 1, auto.assign = FALSE),
    error = function(e) { cat("  Error downloading", TICKER, "\n"); return(NULL) }
  )
  if (is.null(precio_accion)) next

  precio_df <- data.frame(
    date   = index(precio_accion),
    high   = as.numeric(Hi(precio_accion)),
    low    = as.numeric(Lo(precio_accion)),
    close  = as.numeric(Cl(precio_accion)),
    volume = as.numeric(Vo(precio_accion))
  ) %>%
    mutate(
      RET    = log(close / lag(close)) * 100,
      VOL    = (log(high) - log(low))^2 / (4 * log(2)) * 10000,
      VOLUME = log(volume)
    )

  ma_var_vol    <- paste0("VOL_MA",    MA_DIAS)
  ma_var_volume <- paste0("VOLUME_MA", MA_DIAS)

  precio_df <- precio_df %>%
    mutate(
      !!ma_var_vol    := lag(zoo::rollmean(VOL,    k = MA_DIAS, fill = NA, align = "right")),
      !!ma_var_volume := lag(zoo::rollmean(VOLUME, k = MA_DIAS, fill = NA, align = "right"))
    )

  cat("  Prices:", nrow(precio_df), "obs\n")

  # DJI (downloaded once)
  if (is.null(dji_df_global)) {
    DJI_data <- getSymbols("^DJI", from = as.Date("2020-01-01"),
                           to = Sys.Date(), auto.assign = FALSE)
    dji_df_global <- data.frame(
      date           = index(DJI_data),
      DJI_close      = as.numeric(Cl(DJI_data)),
      DJI_high       = as.numeric(Hi(DJI_data)),
      DJI_low        = as.numeric(Lo(DJI_data)),
      DJI_volume_raw = as.numeric(Vo(DJI_data))
    ) %>%
      mutate(
        DJI_RET    = log(DJI_close / lag(DJI_close)) * 100,
        DJI_VOL    = (log(DJI_high) - log(DJI_low))^2 / (4 * log(2)) * 10000,
        DJI_VOLUME = log(DJI_volume_raw)
      )
    cat("  DJI loaded (global)\n")
  }

  # C.4 Loop over algorithms x strategies
  cols_s1       <- names(news_s1)[grepl("^s1_.*_score$", names(news_s1))]
  algos_en_csv  <- gsub("^s1_(.*)_score$", "\\1", cols_s1)
  algos_validos <- intersect(ALGORITMOS_TODOS, algos_en_csv)
  cat("  Algorithms:", paste(algos_validos, collapse = ", "), "\n")

  # Same formula as the comments analysis: wt_sent_pos = (n_pos/n_total) * conf_mean_pos.
  # This is robust to binary algorithms (no neutral), because conf_mean_pos and
  # conf_mean_neg are means WITHIN each label subgroup and vary day to day,
  # avoiding the perfect collinearity of weighted.mean(label==X, w=conf).
  agregar_diario <- function(df, score_col, conf_col, label_col) {
    df %>%
      mutate(
        score = suppressWarnings(as.numeric(.data[[score_col]])),
        conf  = suppressWarnings(as.numeric(.data[[conf_col]])),
        label = .data[[label_col]]
      ) %>%
      filter(!is.na(score), !is.na(conf), !is.na(trading_day)) %>%
      group_by(trading_day) %>%
      summarise(
        sent_wt       = weighted.mean(score, w = conf, na.rm = TRUE),
        n_total       = n(),
        n_pos         = sum(label == "positive", na.rm = TRUE),
        n_neg         = sum(label == "negative", na.rm = TRUE),
        conf_mean_pos = mean(conf[label == "positive"], na.rm = TRUE),
        conf_mean_neg = mean(conf[label == "negative"], na.rm = TRUE),
        n_noticias    = n(),
        .groups       = "drop"
      ) %>%
      mutate(
        sent_pos = (n_pos / n_total) * replace_na(conf_mean_pos, 0),
        sent_neg = -(n_neg / n_total) * replace_na(conf_mean_neg, 0)
      ) %>%
      arrange(trading_day) %>%
      mutate(
        shift     = sent_wt  - lag(sent_wt),
        shift_pos = sent_pos - lag(sent_pos),
        shift_neg = sent_neg - lag(sent_neg)
      )
  }

  for (ALGORITMO in algos_validos) {

    cat("    ->", ALGORITMO, "\n")

    for (ESTRAT in ESTRATEGIAS) {

      strat_low  <- tolower(ESTRAT)
      strat_up   <- toupper(ESTRAT)
      news_strat <- if (ESTRAT == "S2") news_s2 else news_s1

      score_col <- paste0(strat_low, "_", ALGORITMO, "_score")
      conf_col  <- paste0(strat_low, "_", ALGORITMO, "_confidence")
      label_col <- paste0(strat_low, "_", ALGORITMO, "_label")

      if (!all(c(score_col, conf_col, label_col) %in% names(news_strat))) {
        cat("       ", ESTRAT, "missing cols\n"); next
      }

      daily <- agregar_diario(news_strat, score_col, conf_col, label_col) %>%
        mutate(ln_noticias = log(replace_na(n_noticias, 0) + 1))

      cols_precio <- c("date", "RET", "VOL", "VOLUME", ma_var_vol, ma_var_volume)

      data_model <- daily %>%
        inner_join(precio_df %>% select(all_of(cols_precio)),
                   by = c("trading_day" = "date")) %>%
        inner_join(dji_df_global %>% select(date, DJI_RET, DJI_VOL, DJI_VOLUME),
                   by = c("trading_day" = "date")) %>%
        arrange(trading_day) %>%
        mutate(
          NWK = if_else(row_number() == 1 | (trading_day - lag(trading_day)) > 1, 1, 0)
        ) %>%
        filter(!is.na(RET), !is.na(DJI_RET))

      # Rename sentiment variables: <algo>_<sX>_<suffix>
      for (v in c("shift", "shift_pos", "shift_neg")) {
        if (v %in% names(data_model)) {
          new_name <- paste0(ALGORITMO, "_", strat_low, "_", v)
          names(data_model)[names(data_model) == v] <- new_name
        }
      }

      ms <- function(v) paste0(ALGORITMO, "_", strat_low, "_", v)

      ctrl_RET    <- "DJI_RET + NWK + ln_noticias"
      ctrl_VOL    <- paste0("DJI_VOL + NWK + ln_noticias + ", ma_var_vol)
      ctrl_VOLUME <- paste0("DJI_VOLUME + NWK + ln_noticias + ", ma_var_volume)

      pref <- paste0("M", strat_up)  # MS1, MS2

      MODELOS <- list()
      MODELOS[[paste0(pref, "A_RET")]]    <- paste0("RET ~ ",    ctrl_RET,    " + ", ms("shift"))
      MODELOS[[paste0(pref, "A_VOL")]]    <- paste0("VOL ~ ",    ctrl_VOL,    " + ", ms("shift"))
      MODELOS[[paste0(pref, "A_VOLUME")]] <- paste0("VOLUME ~ ", ctrl_VOLUME, " + ", ms("shift"))
      MODELOS[[paste0(pref, "B_RET")]]    <- paste0("RET ~ ",    ctrl_RET,    " + ", ms("shift_pos"), " + ", ms("shift_neg"))
      MODELOS[[paste0(pref, "B_VOL")]]    <- paste0("VOL ~ ",    ctrl_VOL,    " + ", ms("shift_pos"), " + ", ms("shift_neg"))
      MODELOS[[paste0(pref, "B_VOLUME")]] <- paste0("VOLUME ~ ", ctrl_VOLUME, " + ", ms("shift_pos"), " + ", ms("shift_neg"))

      n_estimados <- 0
      for (nombre_modelo in names(MODELOS)) {
        res <- estimar_modelo(MODELOS[[nombre_modelo]], data_model,
                              nombre_modelo, TICKER, ALGORITMO, ESTRAT)
        if (!is.null(res)) {
          RESULTADOS_ALL <- rbind(RESULTADOS_ALL, res)
          n_estimados <- n_estimados + 1
        }
      }
      cat("       ", ESTRAT, "ok (", n_estimados, "models)\n")
    }
  }
}

save(RESULTADOS_ALL, file = file.path(DIR_OUTPUT, "RESULTADOS_NEWS_v1.0.RData"))
write.csv(RESULTADOS_ALL, file.path(DIR_OUTPUT, "RESULTADOS_NEWS_v1.0.csv"),
          row.names = FALSE)
cat("\nRData and CSV saved:", nrow(RESULTADOS_ALL), "rows\n")
```

```{r diagnostico_N, results='asis'}
empresas_disponibles <- intersect(TICKERS, unique(RESULTADOS_ALL$Empresa))

cat("Companies with results:", length(empresas_disponibles), "\n\n")

resumen_N <- RESULTADOS_ALL %>%
  filter(Algoritmo == ALGO_PRINCIPAL, Estrategia == "S2") %>%
  group_by(Empresa, Modelo) %>%
  summarise(N = first(N), .groups = "drop") %>%
  pivot_wider(names_from = Modelo, values_from = N)

if (nrow(resumen_N) > 0) {
  print(kable(resumen_N, caption = paste0("N per company and model (",
              ALGO_LABELS[ALGO_PRINCIPAL], ", S2 Smart-weighted)")))
}
```

# =============================================================================
# PART D: FIRST TABLES - DECOMPOSITION A vs B (S1 + S2 per company)
# =============================================================================

## Structure

One table per company with four columns: **S1-A | S1-B | S2-A | S2-B**.

- **Model A** (parallel to M1 of comments): net $\Delta S$.
- **Model B** (parallel to M3): $\Delta S^{+}$ / $\Delta S^{-}$ decomposition.
- **S1** = title-only; **S2** = smart-weighted.

There is no M2 (AH/PM) equivalent because of the **mandatory lag**: news items are
assigned to the next trading day without distinguishing a period, since their
timestamps are unreliable.

```{r cargar_rdata}
# Uncomment to regenerate tables without re-estimating:
# load(file.path(DIR_OUTPUT, "RESULTADOS_NEWS_v1.0.RData"))
# empresas_disponibles <- intersect(TICKERS, unique(RESULTADOS_ALL$Empresa))
```

```{r funcion_tabla_descomp}
# Decomposition table S1+S2 x A/B for ONE company.
#   Columns:   Variable | S1-A | S1-B | S2-A | S2-B
#   pack_rows: RET / VOL / VOLUME -> Sentiment / Controls / Fit
#   Cell:      coef + stars (NA -> "—" if dropped by collinearity)
construir_tabla_descomp <- function(resultados, empresa, algoritmo) {

  res <- resultados %>% filter(Empresa == empresa, Algoritmo == algoritmo)
  if (nrow(res) == 0) return(NULL)

  ma_vol_v    <- paste0("VOL_MA",    MA_DIAS)
  ma_volume_v <- paste0("VOLUME_MA", MA_DIAS)

  # Return the cell, matching by model + qualified variable name
  # (with the algorithm_<sX>_ prefix) or unqualified (controls).
  get_celda <- function(modelo, var_buscar) {
    fila <- res %>% filter(Modelo == modelo, Variable == var_buscar)
    if (nrow(fila) == 0) return("")
    fmt_celda(fila$Coef[1], fila$P_value[1])
  }

  get_stat <- function(modelo, stat) {
    sub <- res %>% filter(Modelo == modelo) %>% slice(1)
    if (nrow(sub) == 0) return("")
    switch(stat,
      "AICc"   = formatC(sub$AICc,   format = "f", digits = 2),
      "BIC"    = formatC(sub$BIC,    format = "f", digits = 2),
      "R2_adj" = formatC(sub$R2_adj, format = "f", digits = 4)
    )
  }

  # Model and qualified-variable names per strategy
  qual_var <- function(strat_low, sufijo) paste0(algoritmo, "_", strat_low, "_", sufijo)

  estrats <- list(
    list(label = "S1", strat_low = "s1", pref = "MS1"),
    list(label = "S2", strat_low = "s2", pref = "MS2")
  )

  dvs <- list(
    list(nombre = "RET",
         dv_suf = "RET",
         ctrl   = c("(Intercept)", "DJI_RET", "NWK", "ln_noticias")),
    list(nombre = "VOL",
         dv_suf = "VOL",
         ctrl   = c("(Intercept)", "DJI_VOL", "NWK", "ln_noticias", ma_vol_v)),
    list(nombre = "VOLUME",
         dv_suf = "VOLUME",
         ctrl   = c("(Intercept)", "DJI_VOLUME", "NWK", "ln_noticias", ma_volume_v))
  )

  if (knitr::is_latex_output()) {
    stats_disp <- c("AICc", "BIC", "$R^2$ adj")
  } else {
    stats_disp <- c("AICc", "BIC", "R² adj")
  }
  stats_keys <- c("AICc", "BIC", "R2_adj")

  # Sentiment variables in row order (display names come from nombre_var_display())
  sent_filas <- c("shift", "shift_pos", "shift_neg")
  # ...and the column each row maps to (A or B)
  col_de_sent <- c(shift = "A", shift_pos = "B", shift_neg = "B")

  filas    <- list()
  pack_vd  <- list()
  pack_cat <- list()
  row_idx  <- 0
  n_obs    <- NA

  for (dv in dvs) {
    dv_start <- row_idx + 1

    # Sentiment
    cat_sent_start <- row_idx + 1
    for (sf in sent_filas) {
      v_display <- nombre_var_display(sf)
      vals <- c(v_display)
      for (e in estrats) {
        m_a <- paste0(e$pref, "A_", dv$dv_suf)
        m_b <- paste0(e$pref, "B_", dv$dv_suf)
        var_q <- qual_var(e$strat_low, sf)
        c_a <- if (col_de_sent[sf] == "A") get_celda(m_a, var_q) else ""
        c_b <- if (col_de_sent[sf] == "B") get_celda(m_b, var_q) else ""
        vals <- c(vals, c_a, c_b)
      }
      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Sentiment", start = cat_sent_start, end = row_idx)

    # Controls
    cat_ctrl_start <- row_idx + 1
    for (v in dv$ctrl) {
      v_display <- nombre_var_display(v)
      vals <- c(v_display)
      for (e in estrats) {
        m_a <- paste0(e$pref, "A_", dv$dv_suf)
        m_b <- paste0(e$pref, "B_", dv$dv_suf)
        vals <- c(vals, get_celda(m_a, v), get_celda(m_b, v))
      }
      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Controls", start = cat_ctrl_start, end = row_idx)

    # Fit
    cat_adj_start <- row_idx + 1
    for (i in seq_along(stats_disp)) {
      vals <- c(stats_disp[i])
      for (e in estrats) {
        m_a <- paste0(e$pref, "A_", dv$dv_suf)
        m_b <- paste0(e$pref, "B_", dv$dv_suf)
        vals <- c(vals, get_stat(m_a, stats_keys[i]), get_stat(m_b, stats_keys[i]))
      }
      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Fit", start = cat_adj_start, end = row_idx)

    if (is.na(n_obs)) {
      sub_n <- res %>% filter(Modelo == paste0("MS2A_", dv$dv_suf)) %>% slice(1)
      if (nrow(sub_n) == 0) sub_n <- res %>% filter(Modelo == paste0("MS1A_", dv$dv_suf)) %>% slice(1)
      if (nrow(sub_n) > 0) n_obs <- sub_n$N
    }

    pack_vd[[length(pack_vd) + 1]] <- list(
      label = dv$nombre, start = dv_start, end = row_idx)
  }

  tabla_df <- do.call(rbind, filas) %>% as.data.frame(stringsAsFactors = FALSE)
  colnames(tabla_df) <- c("Variable", "S1_A", "S1_B", "S2_A", "S2_B")

  list(tabla = tabla_df, pack_vd = pack_vd, pack_cat = pack_cat, n_obs = n_obs)
}

cat("Function construir_tabla_descomp defined\n")
```

```{r tablas_descomp, results='asis'}
tabla_num <- 0
fmt    <- if (knitr::is_latex_output()) "latex" else "html"
es_pdf <- (fmt == "latex")

es_binario <- ALGO_PRINCIPAL %in% ALGORITMOS_BINARIOS

for (emp in empresas_disponibles) {

  tabla_num <- tabla_num + 1
  resultado <- construir_tabla_descomp(RESULTADOS_ALL, emp, ALGO_PRINCIPAL)

  if (is.null(resultado)) {
    cat(paste0("\n\n### Table ", tabla_num, ": ", emp, " - no data\n\n"))
    next
  }

  tbl <- kbl(resultado$tabla,
      format    = fmt,
      caption   = paste0("A vs B decomposition of news sentiment -- ",
                         emp, " (", ALGO_LABELS[ALGO_PRINCIPAL], ")"),
      col.names = c("", "A", "B", "A", "B"),
      align     = c("l", rep("c", 4)),
      booktabs  = TRUE,
      linesep   = "",
      escape    = FALSE)

  if (es_pdf) {
    tbl <- tbl %>%
      kable_styling(latex_options = c("HOLD_position"), font_size = 9)
  } else {
    tbl <- tbl %>%
      kable_classic(full_width = FALSE, html_font = "Cambria", font_size = 13) %>%
      column_spec(1, width = "9em") %>%
      column_spec(2, width = "8em", border_left = TRUE) %>%
      column_spec(3, width = "8em", border_left = "1px solid #ddd") %>%
      column_spec(4, width = "8em", border_left = TRUE) %>%
      column_spec(5, width = "8em", border_left = "1px solid #ddd")
  }

  tbl <- tbl %>%
    add_header_above(c(" " = 1,
                       "S1 (title-only)"    = 2,
                       "S2 (smart-weighted)" = 2),
                     bold = TRUE, line = TRUE)

  for (g in resultado$pack_vd) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = TRUE, italic = FALSE,
                hline_before = TRUE, hline_after = FALSE,
                latex_gap_space = "0.3em")
  }

  for (g in resultado$pack_cat) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = FALSE, italic = TRUE,
                hline_before = FALSE, hline_after = FALSE,
                indent = FALSE,
                latex_gap_space = "0.1em")
  }

  tbl <- tbl %>%
    footnote(
      general = paste0("N = ", resultado$n_obs, " trading days.\\ ",
                       "*** p<0.001  ** p<0.01  * p<0.05  $\\dagger$ p<0.1."),
      footnote_as_chunk = TRUE,
      threeparttable    = es_pdf,
      escape            = FALSE
    )

  print(tbl)
}

n_tablas_descomp <- tabla_num
```

# =============================================================================
# PART E: SECOND TABLES - ALGORITHM COMPARISON (one per company, S2)
# =============================================================================

```{r funcion_tabla_algos}
# Algorithm-comparison table for ONE company.
# Model B in strategy S2 only, sentiment variables only. Controls are estimated
# but not reported.
#   Columns:    Variable | FinBERT | RoBERTa-Soc | ... | BERT
#   add_header: "Sentiment algorithm" over the columns
#   pack_rows:  "RET", "VOL", "VOLUME"
construir_tabla_algos <- function(resultados, empresa, algoritmos, algo_labels,
                                  estrategia = "S2", modelo = "B") {

  res <- resultados %>% filter(Empresa == empresa, Estrategia == estrategia)
  if (nrow(res) == 0) return(NULL)

  algos_ok <- intersect(algoritmos, unique(res$Algoritmo))
  if (length(algos_ok) == 0) return(NULL)

  strat_low <- tolower(estrategia)
  pref      <- paste0("M", toupper(estrategia))

  if (modelo == "A") {
    vars_sent  <- c("shift")
    modelo_suf <- "A"
  } else {
    vars_sent  <- c("shift_pos", "shift_neg")
    modelo_suf <- "B"
  }

  dvs <- list(
    list(nombre = "RET",    dv_suf = "RET"),
    list(nombre = "VOL",    dv_suf = "VOL"),
    list(nombre = "VOLUME", dv_suf = "VOLUME")
  )

  if (knitr::is_latex_output()) {
    stats_disp <- c("AICc", "BIC", "$R^2$ adj")
  } else {
    stats_disp <- c("AICc", "BIC", "R² adj")
  }
  stats_keys <- c("AICc", "BIC", "R2_adj")

  filas <- list()
  pack_grupos <- list()
  sent_boundary_rows <- c()
  row_idx <- 0
  n_obs <- NA

  for (dv in dvs) {
    dv_start   <- row_idx + 1
    modelo_key <- paste0(pref, modelo_suf, "_", dv$dv_suf)

    for (v in vars_sent) {
      v_display <- nombre_var_display(v)
      vals <- c(v_display)

      for (algo in algos_ok) {
        var_buscar <- paste0(algo, "_", strat_low, "_", v)
        fila <- res %>% filter(Modelo == modelo_key, Algoritmo == algo,
                               Variable == var_buscar)
        if (nrow(fila) == 0) {
          vals <- c(vals, "")
        } else {
          vals <- c(vals, fmt_celda(fila$Coef[1], fila$P_value[1]))
        }
      }

      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }

    sent_boundary_rows <- c(sent_boundary_rows, row_idx)

    for (i in seq_along(stats_disp)) {
      vals <- c(stats_disp[i])
      for (algo in algos_ok) {
        sub <- res %>% filter(Modelo == modelo_key, Algoritmo == algo) %>% slice(1)
        if (nrow(sub) == 0) {
          vals <- c(vals, "")
        } else {
          val <- switch(stats_keys[i],
            "AICc"   = formatC(sub$AICc,   format = "f", digits = 2),
            "BIC"    = formatC(sub$BIC,    format = "f", digits = 2),
            "R2_adj" = formatC(sub$R2_adj, format = "f", digits = 4)
          )
          vals <- c(vals, val)
        }
      }
      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }

    if (is.na(n_obs)) {
      sub_n <- res %>% filter(Modelo == modelo_key) %>% slice(1)
      if (nrow(sub_n) > 0) n_obs <- sub_n$N
    }

    pack_grupos[[length(pack_grupos) + 1]] <- list(
      label = dv$nombre, start = dv_start, end = row_idx)
  }

  tabla_df <- do.call(rbind, filas) %>% as.data.frame(stringsAsFactors = FALSE)
  colnames(tabla_df) <- c("Variable", algo_labels[algos_ok])

  list(tabla = tabla_df, pack_grupos = pack_grupos, algos_usados = algos_ok,
       n_obs = n_obs, sent_boundary_rows = sent_boundary_rows)
}

cat("Function construir_tabla_algos defined\n")
```

```{r tablas_algos, results='asis'}
for (emp in empresas_disponibles) {

  tabla_num <- tabla_num + 1
  resultado <- construir_tabla_algos(RESULTADOS_ALL, emp, ALGORITMOS_TODOS,
                                     ALGO_LABELS, estrategia = "S2")

  if (is.null(resultado)) {
    cat(paste0("\n\n### Table ", tabla_num, ": ", emp, " - no data\n\n"))
    next
  }

  n_algos <- length(resultado$algos_usados)

  tbl <- kbl(resultado$tabla,
      format    = fmt,
      caption   = paste0("Algorithm comparison -- ", emp,
                         " (Model B: $\\Delta$S$\\pm$ news, S2 Smart-weighted)"),
      col.names = c("", colnames(resultado$tabla)[-1]),
      align     = c("l", rep("c", n_algos)),
      booktabs  = TRUE,
      linesep   = "",
      escape    = FALSE)

  if (es_pdf) {
    tbl <- tbl %>%
      kable_styling(latex_options = c("HOLD_position", "scale_down"),
                    font_size = 8)
  } else {
    tbl <- tbl %>%
      kable_classic(full_width = FALSE, html_font = "Cambria", font_size = 13) %>%
      column_spec(1, width = "7em") %>%
      column_spec(2, border_left = TRUE)
    if (n_algos > 1) {
      for (col_i in 3:(n_algos + 1)) {
        tbl <- tbl %>% column_spec(col_i, border_left = "1px solid #ddd")
      }
    }
    for (br in resultado$sent_boundary_rows) {
      tbl <- tbl %>% row_spec(br, extra_css = "border-bottom: 1px solid #ddd;")
    }
  }

  tbl <- tbl %>%
    add_header_above(c(" " = 1, "Sentiment algorithm" = n_algos),
                     bold = TRUE, line = TRUE)

  for (g in resultado$pack_grupos) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = TRUE, italic = FALSE,
                hline_before = TRUE, hline_after = FALSE,
                latex_gap_space = "0.3em")
  }

  tbl <- tbl %>%
    footnote(
      general = paste0("N = ", resultado$n_obs, " trading days.\\ ",
                       "*** p<0.001  ** p<0.01  * p<0.05  $\\dagger$ p<0.1."),
      footnote_as_chunk = TRUE,
      threeparttable    = es_pdf,
      escape            = FALSE
    )

  print(tbl)
}
```

# =============================================================================
# PART F: EXPORT
# =============================================================================

```{r exportar_csv}
write.csv(RESULTADOS_ALL,
          file.path(DIR_OUTPUT, "RESULTADOS_NEWS_v1.0.csv"),
          row.names = FALSE)
cat("CSV saved at:", file.path(DIR_OUTPUT, "RESULTADOS_NEWS_v1.0.csv"), "\n")
```

```{r guardar_helper_manuscrito}
empresas_disponibles <- intersect(TICKERS, unique(RESULTADOS_ALL$Empresa))

helper_news_v1 <- list(
  RESULTADOS_ALL          = RESULTADOS_ALL,
  fmt_celda               = fmt_celda,
  nombre_var_display      = nombre_var_display,
  construir_tabla_descomp = construir_tabla_descomp,
  construir_tabla_algos   = construir_tabla_algos,
  ALGO_PRINCIPAL          = ALGO_PRINCIPAL,
  ALGO_LABELS             = ALGO_LABELS,
  TICKERS                 = TICKERS,
  MA_DIAS                 = MA_DIAS,
  ALGORITMOS_TODOS        = ALGORITMOS_TODOS,
  ESTRATEGIAS             = ESTRATEGIAS,
  ESTRAT_LABELS           = ESTRAT_LABELS,
  ALGORITMOS_BINARIOS     = ALGORITMOS_BINARIOS,
  empresas_disponibles    = empresas_disponibles
)
saveRDS(helper_news_v1, file.path(DIR_OUTPUT, "helper_tablas_news_v1.rds"))
cat("helper_tablas_news_v1.rds saved in", DIR_OUTPUT, "\n")
```
