---
title: "Multi-company analysis: comment-sentiment tables"
author: "Yelko Bejarano"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: cosmo
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{array}
  - \usepackage{colortbl}
  - \usepackage{xcolor}
  - \usepackage{threeparttable}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 8
)

# Detect output format to adapt tables
is_latex <- knitr::is_latex_output()
```

# =============================================================================
# PART A: CONFIGURATION
# =============================================================================

```{r config_principal}
TICKERS <- c("AAPL", "AMD", "AMZN", "DIS", "GOOGL", "META", "MSFT", "NFLX", "NVDA", "TSLA")

ALGO_PRINCIPAL <- "roberta_stocks"

ALGORITMOS_TODOS <- c(
  "finbert", "roberta_social", "roberta_stocks",
  "distilroberta_fin", "bert_sentiment"
)

MA_DIAS <- 7

DIR_BASE <- getwd()
DIR_OUTPUT <- file.path(DIR_BASE, "results")
if (!dir.exists(DIR_OUTPUT)) dir.create(DIR_OUTPUT, recursive = TRUE)

ALGO_LABELS <- c(
  "finbert"           = "FinBERT",
  "roberta_social"    = "RoBERTa-Soc",
  "roberta_stocks"    = "RoBERTa-Stk",
  "distilroberta_fin" = "DistilRoB",
  "bert_sentiment"    = "BERT"
)

cat("=======================================================================\n")
cat("                    CONFIGURATION\n")
cat(sprintf("  Companies:       %s\n", paste(TICKERS, collapse = ", ")))
cat(sprintf("  Primary algo:    %s\n", ALGO_PRINCIPAL))
cat(sprintf("  MA control:      MA(%d)\n", MA_DIAS))
cat("=======================================================================\n")
```

```{r librerias}
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(readr)
  library(lmtest)
  library(sandwich)
  library(car)
  library(tseries)
  library(quantmod)
  library(knitr)
  library(kableExtra)
  library(zoo)
})
cat("Libraries loaded\n")
```

# =============================================================================
# PART B: HELPER FUNCTIONS
# =============================================================================

```{r funciones_estimacion}
# Estimate OLS with Newey-West HAC standard errors (with diagnostics)
estimar_modelo <- function(formula_str, data, nombre_modelo, ticker, algoritmo) {
  formula_str <- gsub("\\s+", " ", formula_str)
  formula_modelo <- as.formula(formula_str)
  vars_en_formula <- all.vars(formula_modelo)

  vars_faltantes <- setdiff(vars_en_formula, names(data))
  if (length(vars_faltantes) > 0) {
    cat("      [!]", nombre_modelo, "-> MISSING VARS:",
        paste(vars_faltantes, collapse = ", "), "\n")
    return(NULL)
  }

  data_est <- data %>% select(all_of(vars_en_formula)) %>% na.omit()
  if (nrow(data_est) < 30) {
    cat("      [!]", nombre_modelo, "-> only", nrow(data_est), "obs (min 30)\n")
    return(NULL)
  }

  modelo_ols <- lm(formula_modelo, data = data_est)
  robust_se <- NeweyWest(modelo_ols, prewhite = FALSE, adjust = TRUE)
  coef_robust <- coeftest(modelo_ols, vcov = robust_se)

  n_obs <- nrow(data_est)
  k_params <- length(coef(modelo_ols))
  r2_adj <- summary(modelo_ols)$adj.r.squared
  aic_val <- AIC(modelo_ols)
  aicc_val <- aic_val + (2 * k_params^2 + 2 * k_params) / (n_obs - k_params - 1)
  bic_val <- BIC(modelo_ols)

  resultados <- data.frame()
  for (i in 1:nrow(coef_robust)) {
    var_name <- rownames(coef_robust)[i]
    p_val <- coef_robust[i, "Pr(>|t|)"]
    sig_symbol <- ifelse(p_val < 0.001, "***",
                  ifelse(p_val < 0.01, "**",
                  ifelse(p_val < 0.05, "*",
                  ifelse(p_val < 0.1, "†", ""))))

    resultados <- rbind(resultados, data.frame(
      Modelo = nombre_modelo,
      Empresa = ticker,
      Algoritmo = algoritmo,
      N = n_obs,
      Variable = var_name,
      Coef = coef_robust[i, "Estimate"],
      Std_Error = coef_robust[i, "Std. Error"],
      t_value = coef_robust[i, "t value"],
      P_value = p_val,
      Signif = sig_symbol,
      AICc = aicc_val,
      BIC = bic_val,
      R2_adj = r2_adj,
      stringsAsFactors = FALSE
    ))
  }

  # Variables dropped by perfect collinearity (NA in coef(lm)) are recorded with
  # Coef = NA so the table shows "—" instead of an empty cell.
  coefs_lm <- coef(modelo_ols)
  vars_descartadas <- names(coefs_lm)[is.na(coefs_lm)]
  for (var_name in vars_descartadas) {
    resultados <- rbind(resultados, data.frame(
      Modelo     = nombre_modelo,
      Empresa    = ticker,
      Algoritmo  = algoritmo,
      N          = n_obs,
      Variable   = var_name,
      Coef       = NA_real_,
      Std_Error  = NA_real_,
      t_value    = NA_real_,
      P_value    = NA_real_,
      Signif     = "",
      AICc       = aicc_val,
      BIC        = bic_val,
      R2_adj     = r2_adj,
      stringsAsFactors = FALSE
    ))
  }

  return(resultados)
}

# Format a table cell = coefficient + significance stars
fmt_celda <- function(coef, pval, digits = 4) {
  if (is.na(coef)) return("—")  # dropped by collinearity
  if (is.na(pval)) return(formatC(coef, format = "f", digits = digits))
  dag <- if (knitr::is_latex_output()) "$\\dagger$" else "†"
  stars <- ifelse(pval < 0.001, "***",
           ifelse(pval < 0.01, "**",
           ifelse(pval < 0.05, "*",
           ifelse(pval < 0.1, dag, ""))))
  coef_str <- formatC(coef, format = "f", digits = digits)
  paste0(coef_str, stars)
}

# Display name for a variable (without the algorithm prefix)
nombre_var_display <- function(var_raw, algoritmo = NULL) {
  v <- var_raw
  if (!is.null(algoritmo)) v <- gsub(paste0("^", algoritmo, "_"), "", v)

  # LaTeX: real math superscripts ($\Delta S^{+}$) in the PDF.
  # HTML:  Unicode (Δ, ⁺/⁻) for the browser.
  if (knitr::is_latex_output()) {
    lookup <- c(
      "(Intercept)"                = "Intercept",
      "DJI_RET"                    = "DJI RET",
      "DJI_VOL"                    = "DJI VOL",
      "DJI_VOLUME"                 = "DJI VOLUME",
      "NWK"                        = "NWK",
      "ln_comments_fuera_mercado"  = "ln(comments)",
      "wt_shift_fuera_mercado"     = "$\\Delta S$ ON",
      "wt_shift_afterhours"        = "$\\Delta S$ AH",
      "wt_shift_premarket"         = "$\\Delta S$ PM",
      "wt_shift_pos_afterhours"    = "$\\Delta S^{+}$ AH",
      "wt_shift_neg_afterhours"    = "$\\Delta S^{-}$ AH",
      "wt_shift_pos_premarket"     = "$\\Delta S^{+}$ PM",
      "wt_shift_neg_premarket"     = "$\\Delta S^{-}$ PM"
    )
  } else {
    lookup <- c(
      "(Intercept)"                = "Intercept",
      "DJI_RET"                    = "DJI RET",
      "DJI_VOL"                    = "DJI VOL",
      "DJI_VOLUME"                 = "DJI VOLUME",
      "NWK"                        = "NWK",
      "ln_comments_fuera_mercado"  = "ln(comments)",
      "wt_shift_fuera_mercado"     = "ΔS ON",
      "wt_shift_afterhours"        = "ΔS AH",
      "wt_shift_premarket"         = "ΔS PM",
      "wt_shift_pos_afterhours"    = "ΔS⁺ AH",
      "wt_shift_neg_afterhours"    = "ΔS⁻ AH",
      "wt_shift_pos_premarket"     = "ΔS⁺ PM",
      "wt_shift_neg_premarket"     = "ΔS⁻ PM"
    )
  }

  if (v %in% names(lookup)) return(lookup[v])
  if (grepl("^VOL_MA", v)) return(paste0("VOL MA(", MA_DIAS, ")"))
  if (grepl("^VOLUME_MA", v)) return(paste0("VOL. MA(", MA_DIAS, ")"))
  return(v)
}

# Guarantee the expected columns exist after pivot_wider
asegurar_columnas <- function(df) {
  for (p in c("afterhours", "premarket", "market")) {
    for (prefix in c("sentiment_wt_", "n_comments_", "wt_sent_pos_", "wt_sent_neg_")) {
      col <- paste0(prefix, p)
      if (!col %in% names(df)) df[[col]] <- NA_real_
    }
  }
  return(df)
}

cat("Helper functions defined\n")
```

# =============================================================================
# PART C: MAIN LOOP - PER-COMPANY PROCESSING
# =============================================================================

```{r bucle_empresas, results='hide'}
RESULTADOS_ALL <- data.frame()
dji_df_global <- NULL

cat("=======================================================================\n")
cat("              PER-COMPANY PROCESSING\n")
cat("=======================================================================\n\n")

for (TICKER in TICKERS) {

  cat("\n=====================================================\n")
  cat(sprintf("  COMPANY: %-38s\n", TICKER))
  cat("=====================================================\n")

  # C.1 Load comments
  comments_file <- file.path(DIR_BASE, TICKER,
                             paste0("comments_", tolower(TICKER), "_all_sentiments.csv"))

  if (!file.exists(comments_file)) {
    cat("  FILE NOT FOUND:", comments_file, "\n")
    next
  }

  comments_raw <- read_csv(comments_file, show_col_types = FALSE)
  cat("  CSV loaded:", nrow(comments_raw), "comments\n")

  # C.2 Time zone and intraday periods
  comments_raw <- comments_raw %>%
    mutate(
      datetime_spain = force_tz(comment_datetime_full, tzone = "Europe/Madrid"),
      comment_datetime_est = with_tz(datetime_spain, tzone = "America/New_York"),
      comment_hour_decimal = hour(comment_datetime_est) + minute(comment_datetime_est) / 60
    )

  comments <- comments_raw %>%
    mutate(
      periodo = case_when(
        comment_hour_decimal >= 16 ~ "afterhours",
        comment_hour_decimal < 9.5 ~ "premarket",
        TRUE ~ "market"
      ),
      trading_day = trading_date
    ) %>%
    distinct(body, score, trading_day, .keep_all = TRUE)

  cat("  Unique comments:", nrow(comments), "\n")

  # Period distribution diagnostic
  dist_periodo <- comments %>% count(periodo) %>% mutate(pct = round(n / sum(n) * 100, 1))
  for (r in 1:nrow(dist_periodo)) {
    cat(sprintf("      %s: %d (%.1f%%)\n", dist_periodo$periodo[r],
                dist_periodo$n[r], dist_periodo$pct[r]))
  }

  # C.3 Market data
  fecha_min <- min(comments$trading_day)
  fecha_max <- max(comments$trading_day)

  precio_accion <- tryCatch(
    getSymbols(TICKER, from = fecha_min - 30, to = fecha_max + 1, auto.assign = FALSE),
    error = function(e) { cat("  Error downloading", TICKER, "\n"); return(NULL) }
  )
  if (is.null(precio_accion)) next

  precio_df <- data.frame(
    date = index(precio_accion),
    open = as.numeric(Op(precio_accion)),
    high = as.numeric(Hi(precio_accion)),
    low = as.numeric(Lo(precio_accion)),
    close = as.numeric(Cl(precio_accion)),
    volume = as.numeric(Vo(precio_accion))
  ) %>%
    mutate(
      RET = log(close / lag(close)) * 100,
      VOL    = (log(high) - log(low))^2 / (4 * log(2)) * 10000,
      VOLUME = log(volume)
    )

  ma_var_vol <- paste0("VOL_MA", MA_DIAS)
  ma_var_volume <- paste0("VOLUME_MA", MA_DIAS)

  precio_df <- precio_df %>%
    mutate(
      !!ma_var_vol := lag(zoo::rollmean(VOL, k = MA_DIAS, fill = NA, align = "right")),
      !!ma_var_volume := lag(zoo::rollmean(VOLUME, k = MA_DIAS, fill = NA, align = "right"))
    )

  cat("  Prices:", nrow(precio_df), "obs\n")

  # DJI (downloaded once)
  if (is.null(dji_df_global)) {
    DJI_data <- getSymbols("^DJI", from = as.Date("2020-01-01"),
                            to = Sys.Date(), auto.assign = FALSE)
    dji_df_global <- data.frame(
      date = index(DJI_data),
      DJI_close = as.numeric(Cl(DJI_data)),
      DJI_high = as.numeric(Hi(DJI_data)),
      DJI_low = as.numeric(Lo(DJI_data)),
      DJI_volume_raw = as.numeric(Vo(DJI_data))
    ) %>%
      mutate(
        DJI_RET = log(DJI_close / lag(DJI_close)) * 100,
        DJI_VOL    = (log(DJI_high) - log(DJI_low))^2 / (4 * log(2)) * 10000,
        DJI_VOLUME = log(DJI_volume_raw)
      )
    cat("  DJI loaded (global)\n")
  }

  # C.4 Loop over algorithms
  columnas_csv <- names(comments)
  algoritmos_disponibles <- gsub("_score$", "", columnas_csv[grepl("_score$", columnas_csv)])
  algoritmos_validos <- intersect(ALGORITMOS_TODOS, algoritmos_disponibles)
  cat("  Algorithms:", paste(algoritmos_validos, collapse = ", "), "\n")

  for (ALGORITMO in algoritmos_validos) {

    cat("    -> ", ALGORITMO, "...")

    score_var <- paste0(ALGORITMO, "_score")
    conf_var <- paste0(ALGORITMO, "_confidence")
    label_var <- paste0(ALGORITMO, "_label")

    if (!score_var %in% names(comments)) { cat(" SKIPPED\n"); next }

    # Confidence-weighted sentiment per period
    agg_wt_periodo <- comments %>%
      group_by(trading_day, periodo) %>%
      summarise(
        sentiment_wt = weighted.mean(.data[[score_var]], w = .data[[conf_var]], na.rm = TRUE),
        n_comments = n(),
        .groups = 'drop'
      ) %>%
      pivot_wider(
        id_cols = trading_day,
        names_from = periodo,
        values_from = c(sentiment_wt, n_comments),
        names_glue = "{.value}_{periodo}"
      )

    # Positive/negative components.
    # Denominator: sum(conf) over all comments in the period (not n_total).
    # wt_sent_neg is negative: it is the negative contribution to the index.
    agg_pos_neg_periodo <- comments %>%
      group_by(trading_day, periodo) %>%
      summarise(
        sum_conf_total = sum(.data[[conf_var]], na.rm = TRUE),
        sum_conf_pos   = sum(.data[[conf_var]][.data[[label_var]] == "positive"], na.rm = TRUE),
        sum_conf_neg   = sum(.data[[conf_var]][.data[[label_var]] == "negative"], na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      mutate(
        wt_sent_pos = if_else(sum_conf_total > 0, sum_conf_pos / sum_conf_total, 0),
        wt_sent_neg = if_else(sum_conf_total > 0, -sum_conf_neg / sum_conf_total, 0)
      ) %>%
      select(trading_day, periodo, wt_sent_pos, wt_sent_neg) %>%
      pivot_wider(
        id_cols = trading_day,
        names_from = periodo,
        values_from = c(wt_sent_pos, wt_sent_neg),
        names_glue = "{.value}_{periodo}"
      )

    # Join and guarantee columns
    daily_sentiment <- agg_wt_periodo %>%
      left_join(agg_pos_neg_periodo, by = "trading_day") %>%
      arrange(trading_day)

    daily_sentiment <- asegurar_columnas(daily_sentiment)

    # Al-Nasseri et al. (2021, note 16): "filling those missing values with zeros".
    # Impute sentiment LEVELS to 0 BEFORE computing shifts.
    # Rationale: no comments in a period = no new information = neutral.
    level_cols <- c("sentiment_wt_afterhours", "sentiment_wt_premarket",
                     "wt_sent_pos_afterhours", "wt_sent_neg_afterhours",
                     "wt_sent_pos_premarket", "wt_sent_neg_premarket")

    na_levels <- sapply(level_cols, function(x) sum(is.na(daily_sentiment[[x]])))
    for (lc in level_cols) daily_sentiment[[lc]] <- replace_na(daily_sentiment[[lc]], 0)

    # Compute shifts on the imputed levels (no NA propagation)
    daily_sentiment <- daily_sentiment %>%
      mutate(
        wt_shift_afterhours = sentiment_wt_afterhours - lag(sentiment_wt_afterhours),
        wt_shift_premarket = sentiment_wt_premarket - lag(sentiment_wt_premarket),
        wt_shift_fuera_mercado = wt_shift_afterhours + wt_shift_premarket,
        wt_shift_pos_afterhours = wt_sent_pos_afterhours - lag(wt_sent_pos_afterhours),
        wt_shift_pos_premarket = wt_sent_pos_premarket - lag(wt_sent_pos_premarket),
        wt_shift_neg_afterhours = wt_sent_neg_afterhours - lag(wt_sent_neg_afterhours),
        wt_shift_neg_premarket = wt_sent_neg_premarket - lag(wt_sent_neg_premarket),
        ln_comments_fuera_mercado = log(replace_na(n_comments_afterhours, 0) +
                                         replace_na(n_comments_premarket, 0) + 1)
      )

    if (sum(na_levels) > 0) {
      cat(" [levels NA→0: AH=", na_levels["sentiment_wt_afterhours"],
          " PM=", na_levels["sentiment_wt_premarket"], "]")
    }

    # Join with market data
    cols_precio <- c("date", "RET", "VOL", "VOLUME", ma_var_vol, ma_var_volume)

    data_model <- daily_sentiment %>%
      inner_join(precio_df %>% select(all_of(cols_precio)),
                 by = c("trading_day" = "date")) %>%
      inner_join(dji_df_global %>% select(date, DJI_RET, DJI_VOL, DJI_VOLUME),
                 by = c("trading_day" = "date")) %>%
      arrange(trading_day) %>%
      mutate(
        NWK = if_else(row_number() == 1 | (trading_day - lag(trading_day)) > 1, 1, 0)
      ) %>%
      filter(!is.na(RET), !is.na(DJI_RET))

    # Add the algorithm prefix
    vars_a_renombrar <- c(
      "wt_shift_afterhours", "wt_shift_premarket", "wt_shift_fuera_mercado",
      "wt_shift_pos_afterhours", "wt_shift_pos_premarket",
      "wt_shift_neg_afterhours", "wt_shift_neg_premarket"
    )
    for (v in vars_a_renombrar) {
      if (v %in% names(data_model)) {
        names(data_model)[names(data_model) == v] <- paste0(ALGORITMO, "_", v)
      }
    }

    # Define the 9 models (M1/M2/M3 x RET/VOL/VOLUME)
    make_var <- function(s) paste0(ALGORITMO, "_wt_shift_", s)
    make_pos <- function(s) paste0(ALGORITMO, "_wt_shift_pos_", s)
    make_neg <- function(s) paste0(ALGORITMO, "_wt_shift_neg_", s)

    ctrl_RET <- "DJI_RET + NWK + ln_comments_fuera_mercado"
    ctrl_VOL <- paste0("DJI_VOL + NWK + ln_comments_fuera_mercado + ", ma_var_vol)
    ctrl_VOLUME <- paste0("DJI_VOLUME + NWK + ln_comments_fuera_mercado + ", ma_var_volume)

    MODELOS <- list(
      M1_RET = paste0("RET ~ ", ctrl_RET, " + ", make_var("fuera_mercado")),
      M1_VOL = paste0("VOL ~ ", ctrl_VOL, " + ", make_var("fuera_mercado")),
      M1_VOLUME = paste0("VOLUME ~ ", ctrl_VOLUME, " + ", make_var("fuera_mercado")),
      M2_RET = paste0("RET ~ ", ctrl_RET, " + ",
                       make_var("afterhours"), " + ", make_var("premarket")),
      M2_VOL = paste0("VOL ~ ", ctrl_VOL, " + ",
                       make_var("afterhours"), " + ", make_var("premarket")),
      M2_VOLUME = paste0("VOLUME ~ ", ctrl_VOLUME, " + ",
                          make_var("afterhours"), " + ", make_var("premarket")),
      M3_RET = paste0("RET ~ ", ctrl_RET, " + ",
                       make_pos("afterhours"), " + ", make_neg("afterhours"), " + ",
                       make_pos("premarket"), " + ", make_neg("premarket")),
      M3_VOL = paste0("VOL ~ ", ctrl_VOL, " + ",
                       make_pos("afterhours"), " + ", make_neg("afterhours"), " + ",
                       make_pos("premarket"), " + ", make_neg("premarket")),
      M3_VOLUME = paste0("VOLUME ~ ", ctrl_VOLUME, " + ",
                          make_pos("afterhours"), " + ", make_neg("afterhours"), " + ",
                          make_pos("premarket"), " + ", make_neg("premarket"))
    )

    n_estimados <- 0
    for (nombre_modelo in names(MODELOS)) {
      res <- estimar_modelo(MODELOS[[nombre_modelo]], data_model,
                            nombre_modelo, TICKER, ALGORITMO)
      if (!is.null(res)) {
        RESULTADOS_ALL <- rbind(RESULTADOS_ALL, res)
        n_estimados <- n_estimados + 1
      }
    }
    cat(" ", n_estimados, "models\n")
  }

  # Save per-company RData
  resultados_empresa <- RESULTADOS_ALL %>% filter(Empresa == TICKER)
  rdata_file <- file.path(DIR_OUTPUT, paste0(TICKER, "_results.RData"))
  save(resultados_empresa, file = rdata_file)
  cat("  RData:", basename(rdata_file), "\n")
}

save(RESULTADOS_ALL, file = file.path(DIR_OUTPUT, "comments_results.RData"))
cat("\nGlobal RData:", nrow(RESULTADOS_ALL), "rows\n")
cat("  Companies:", paste(unique(RESULTADOS_ALL$Empresa), collapse = ", "), "\n")
```

```{r diagnostico_N, results='asis'}
# Diagnostic: N per company and temporal continuity
cat("\n===================================================================\n")
cat("               DIAGNOSTIC: OBSERVATIONS PER COMPANY\n")
cat("===================================================================\n\n")

# N per company and model (first algorithm as reference)
algo_ref <- ALGORITMOS_TODOS[1]

for (emp in unique(RESULTADOS_ALL$Empresa)) {
  sub <- RESULTADOS_ALL %>% filter(Empresa == emp, Algoritmo == algo_ref)
  modelos_emp <- unique(sub$Modelo)
  n_ref <- sub %>% filter(Modelo == modelos_emp[1]) %>% slice(1) %>% pull(N)

  cat(sprintf("  %s: N = %d", emp, n_ref))

  if (n_ref < 100) {
    cat(" [!] SMALL SAMPLE")
  }
  cat("\n")
}

# Continuity detail for companies with N < 200
cat("\n--- Temporal continuity detail ---\n\n")

empresas_check <- unique(RESULTADOS_ALL$Empresa)

for (emp in empresas_check) {
  sub <- RESULTADOS_ALL %>% filter(Empresa == emp, Algoritmo == algo_ref,
                                     Modelo == "M1_RET")
  n_emp <- if (nrow(sub) > 0) sub$N[1] else NA

  if (!is.na(n_emp) && n_emp < 200) {
    # Rebuild the dataset for this company
    comments_file <- file.path(DIR_BASE, emp,
                               paste0("comments_", tolower(emp), "_all_sentiments.csv"))
    if (file.exists(comments_file)) {
      tmp_raw <- read_csv(comments_file, show_col_types = FALSE)

      # Count trading days with comments
      dias_con_comments <- length(unique(tmp_raw$trading_date))
      rango <- range(tmp_raw$trading_date)

      cat(sprintf("  %s: N = %d | Days with comments: %d | Range: %s to %s\n",
                  emp, n_emp, dias_con_comments, rango[1], rango[2]))

      # Temporal gaps
      dias_ordenados <- sort(unique(tmp_raw$trading_date))
      diffs <- as.numeric(diff(dias_ordenados))
      gaps_largos <- sum(diffs > 5)  # gaps longer than 5 days (1 week)
      max_gap <- max(diffs)
      median_gap <- median(diffs)

      cat(sprintf("    Median between obs: %.0f days | Max gap: %.0f days | Gaps >5 days: %d\n",
                  median_gap, max_gap, gaps_largos))

      if (max_gap > 30) {
        cat("    [!] Gap >30 days detected - series NOT continuous\n")
      } else if (median_gap <= 2) {
        cat("    Observations reasonably consecutive\n")
      }
    }
  }
}

cat("\n")
```

# =============================================================================
# PART D: FIRST TABLES - PROGRESSIVE DECOMPOSITION (one per company)
# =============================================================================

## Structure

One table per company. Variable column + 3 columns (M1, M2, M3).
`add_header_above()` groups M1/M2/M3 on top.
`pack_rows()` on the side groups *Sentiment*, *Controls*, *Fit* within each DV.

```{r cargar_rdata}
# Uncomment to regenerate tables without re-estimating:
# load(file.path(DIR_OUTPUT, "comments_results.RData"))

if (!exists("RESULTADOS_ALL") || nrow(RESULTADOS_ALL) == 0) {
  stop("No results. Run Part C or load the RData.")
}

empresas_disponibles <- intersect(TICKERS, unique(RESULTADOS_ALL$Empresa))
cat("Companies with results:", paste(empresas_disponibles, collapse = ", "), "\n")

empresas_sin_datos <- setdiff(TICKERS, empresas_disponibles)
if (length(empresas_sin_datos) > 0) {
  cat("Without results:", paste(empresas_sin_datos, collapse = ", "), "\n")
}
```

```{r funcion_tabla_descomp}
# Progressive-decomposition table for ONE company.
#   Columns:    Variable | M1 | M2 | M3
#   add_header: "Progressive decomposition" over M1-M3
#   pack_rows:  "RET - Sentiment", "RET - Controls", "RET - Fit", etc.
#   Cell:       coefficient + stars
construir_tabla_descomp <- function(resultados, empresa, algoritmo) {

  res <- resultados %>% filter(Empresa == empresa, Algoritmo == algoritmo)
  if (nrow(res) == 0) return(NULL)

  ma_vol_v <- paste0("VOL_MA", MA_DIAS)
  ma_volume_v <- paste0("VOLUME_MA", MA_DIAS)

  # Internal helpers
  get_celda <- function(modelo, var_raw) {
    var_buscar <- paste0(algoritmo, "_", var_raw)
    fila <- res %>% filter(Modelo == modelo, Variable == var_buscar)
    if (nrow(fila) == 0) fila <- res %>% filter(Modelo == modelo, Variable == var_raw)
    if (nrow(fila) == 0) return("")
    fmt_celda(fila$Coef, fila$P_value)
  }

  get_stat <- function(modelo, stat) {
    sub <- res %>% filter(Modelo == modelo) %>% slice(1)
    if (nrow(sub) == 0) return("")
    switch(stat,
      "AICc"       = formatC(sub$AICc, format = "f", digits = 2),
      "BIC"        = formatC(sub$BIC, format = "f", digits = 2),
      "R² adj" = formatC(sub$R2_adj, format = "f", digits = 4)
    )
  }

  # Definitions
  sent_M1 <- c("wt_shift_fuera_mercado")
  sent_M2 <- c("wt_shift_afterhours", "wt_shift_premarket")
  sent_M3 <- c("wt_shift_pos_afterhours", "wt_shift_neg_afterhours",
                "wt_shift_pos_premarket", "wt_shift_neg_premarket")
  all_sent <- c(sent_M1, sent_M2, sent_M3)

  dvs <- list(
    list(nombre = "RET",    modelos = c("M1_RET", "M2_RET", "M3_RET"),
         ctrl = c("(Intercept)", "DJI_RET", "NWK", "ln_comments_fuera_mercado")),
    list(nombre = "VOL",    modelos = c("M1_VOL", "M2_VOL", "M3_VOL"),
         ctrl = c("(Intercept)", "DJI_VOL", "NWK", "ln_comments_fuera_mercado", ma_vol_v)),
    list(nombre = "VOLUME", modelos = c("M1_VOLUME", "M2_VOLUME", "M3_VOLUME"),
         ctrl = c("(Intercept)", "DJI_VOLUME", "NWK", "ln_comments_fuera_mercado", ma_volume_v))
  )

  stats <- c("AICc", "BIC", "R² adj")

  # Build rows: Variable | M1 | M2 | M3 (no Group column)
  filas <- list()
  pack_vd <- list()     # outer pack_rows: RET / VOL / VOLUME
  pack_cat <- list()    # inner pack_rows: Sentiment / Controls / Fit
  row_idx <- 0
  n_obs <- NA

  for (dv in dvs) {
    m <- dv$modelos
    dv_start <- row_idx + 1

    # Sentiment
    cat_sent_start <- row_idx + 1
    for (v in all_sent) {
      v_display <- nombre_var_display(v)
      c1 <- if (v %in% sent_M1) get_celda(m[1], v) else ""
      c2 <- if (v %in% sent_M2) get_celda(m[2], v) else ""
      c3 <- if (v %in% sent_M3) get_celda(m[3], v) else ""
      row_idx <- row_idx + 1
      filas[[row_idx]] <- c(v_display, c1, c2, c3)
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Sentiment", start = cat_sent_start, end = row_idx)

    # Controls
    cat_ctrl_start <- row_idx + 1
    for (v in dv$ctrl) {
      v_display <- nombre_var_display(v)
      row_idx <- row_idx + 1
      filas[[row_idx]] <- c(v_display, get_celda(m[1], v),
                            get_celda(m[2], v), get_celda(m[3], v))
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Controls", start = cat_ctrl_start, end = row_idx)

    # Fit
    cat_adj_start <- row_idx + 1
    for (s in stats) {
      row_idx <- row_idx + 1
      filas[[row_idx]] <- c(s, get_stat(m[1], s), get_stat(m[2], s), get_stat(m[3], s))
    }
    pack_cat[[length(pack_cat) + 1]] <- list(
      label = "Fit", start = cat_adj_start, end = row_idx)

    # Capture N from the first available model
    if (is.na(n_obs)) {
      sub_n <- res %>% filter(Modelo == m[1]) %>% slice(1)
      if (nrow(sub_n) > 0) n_obs <- sub_n$N
    }

    pack_vd[[length(pack_vd) + 1]] <- list(
      label = dv$nombre, start = dv_start, end = row_idx
    )
  }

  tabla_df <- do.call(rbind, filas) %>% as.data.frame(stringsAsFactors = FALSE)
  colnames(tabla_df) <- c("Variable", "M1", "M2", "M3")

  list(tabla = tabla_df, pack_vd = pack_vd, pack_cat = pack_cat, n_obs = n_obs)
}

cat("Function construir_tabla_descomp defined\n")
```

```{r tablas_descomp, results='asis'}
# Generate progressive-decomposition tables.
# In LaTeX do NOT force column widths: booktabs + align c("l","c","c","c")
# auto-sizes perfectly. column_spec is only for HTML.
tabla_num <- 0
fmt <- if (knitr::is_latex_output()) "latex" else "html"
es_pdf <- (fmt == "latex")

for (emp in empresas_disponibles) {

  tabla_num <- tabla_num + 1
  resultado <- construir_tabla_descomp(RESULTADOS_ALL, emp, ALGO_PRINCIPAL)

  if (is.null(resultado)) {
    cat(paste0("\n\n### Table ", tabla_num, ": ", emp, " - no data\n\n"))
    next
  }

  tbl <- kbl(resultado$tabla,
      format = fmt,
      caption = paste0("Progressive sentiment decomposition -- ", emp,
                       " (", ALGO_LABELS[ALGO_PRINCIPAL], ")"),
      col.names = c("", "M1", "M2", "M3"),
      align = c("l", "c", "c", "c"),
      booktabs = TRUE,
      linesep = "",
      escape = FALSE)

  if (es_pdf) {
    tbl <- tbl %>%
      kable_styling(
        latex_options = c("HOLD_position"),
        font_size = 9
      )
  } else {
    tbl <- tbl %>%
      kable_classic(full_width = FALSE, html_font = "Cambria", font_size = 13) %>%
      column_spec(1, width = "8em") %>%
      column_spec(2, width = "10em", border_left = TRUE) %>%
      column_spec(3, width = "10em", border_left = "1px solid #ddd") %>%
      column_spec(4, width = "10em", border_left = "1px solid #ddd")
  }

  for (g in resultado$pack_vd) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = TRUE, italic = FALSE,
                hline_before = TRUE, hline_after = FALSE,
                latex_gap_space = "0.3em")
  }

  for (g in resultado$pack_cat) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = FALSE, italic = TRUE,
                hline_before = FALSE, hline_after = FALSE,
                indent = FALSE,
                latex_gap_space = "0.1em")
  }

  tbl <- tbl %>%
    footnote(
      general = paste0("N = ", resultado$n_obs, " trading days.\\ ",
                       "*** p<0.001  ** p<0.01  * p<0.05  † p<0.1."),
      footnote_as_chunk = TRUE,
      threeparttable = es_pdf,
      escape = FALSE
    )

  print(tbl)
}

n_tablas_descomp <- tabla_num
```

# =============================================================================
# PART E: SECOND TABLES - ALGORITHM COMPARISON (one per company)
# =============================================================================

```{r funcion_tabla_algos}
# Algorithm-comparison table for ONE company.
# M3 only, sentiment variables only. Controls are estimated but not reported.
#   Columns:    Variable | FinBERT | RoBERTa-Soc | ... | BERT
#   add_header: "Sentiment algorithm" over the algorithm columns
#   pack_rows:  "RET", "VOL", "VOLUME"
construir_tabla_algos <- function(resultados, empresa, algoritmos, algo_labels) {

  res <- resultados %>% filter(Empresa == empresa)
  if (nrow(res) == 0) return(NULL)

  algos_ok <- intersect(algoritmos, unique(res$Algoritmo))
  if (length(algos_ok) == 0) return(NULL)

  vars_sent <- c("wt_shift_pos_afterhours", "wt_shift_neg_afterhours",
                  "wt_shift_pos_premarket", "wt_shift_neg_premarket")

  dvs <- list(
    list(nombre = "RET",    modelo = "M3_RET"),
    list(nombre = "VOL",    modelo = "M3_VOL"),
    list(nombre = "VOLUME", modelo = "M3_VOLUME")
  )

  stats <- c("AICc", "BIC", "R² adj")

  filas <- list()
  pack_grupos <- list()
  sent_boundary_rows <- c()  # rows where sentiment ends (for a faint rule)
  row_idx <- 0
  n_obs <- NA

  for (dv in dvs) {
    dv_start <- row_idx + 1

    # Sentiment variables
    for (v in vars_sent) {
      v_display <- nombre_var_display(v)
      vals <- c(v_display)

      for (algo in algos_ok) {
        var_buscar <- paste0(algo, "_", v)
        fila <- res %>% filter(Modelo == dv$modelo, Algoritmo == algo,
                               Variable == var_buscar)
        if (nrow(fila) == 0) {
          vals <- c(vals, "")
        } else {
          vals <- c(vals, fmt_celda(fila$Coef, fila$P_value))
        }
      }

      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }

    # Mark the last sentiment row
    sent_boundary_rows <- c(sent_boundary_rows, row_idx)

    # Fit statistics
    for (s in stats) {
      vals <- c(s)
      for (algo in algos_ok) {
        sub <- res %>% filter(Modelo == dv$modelo, Algoritmo == algo) %>% slice(1)
        if (nrow(sub) == 0) {
          vals <- c(vals, "")
        } else {
          val <- switch(s,
            "AICc"       = formatC(sub$AICc, format = "f", digits = 2),
            "BIC"        = formatC(sub$BIC, format = "f", digits = 2),
            "R² adj" = formatC(sub$R2_adj, format = "f", digits = 4)
          )
          vals <- c(vals, val)
        }
      }
      row_idx <- row_idx + 1
      filas[[row_idx]] <- vals
    }

    # Capture N
    if (is.na(n_obs)) {
      sub_n <- res %>% filter(Modelo == dv$modelo) %>% slice(1)
      if (nrow(sub_n) > 0) n_obs <- sub_n$N
    }

    pack_grupos[[length(pack_grupos) + 1]] <- list(
      label = dv$nombre, start = dv_start, end = row_idx
    )
  }

  tabla_df <- do.call(rbind, filas) %>% as.data.frame(stringsAsFactors = FALSE)
  colnames(tabla_df) <- c("Variable", algo_labels[algos_ok])

  list(tabla = tabla_df, pack_grupos = pack_grupos, algos_usados = algos_ok,
       n_obs = n_obs, sent_boundary_rows = sent_boundary_rows)
}

cat("Function construir_tabla_algos defined\n")
```

```{r tablas_algos, results='asis'}
# Generate algorithm-comparison tables.
# Same principle: in LaTeX, zero column_spec; perfect auto-sizing.
for (emp in empresas_disponibles) {

  tabla_num <- tabla_num + 1
  resultado <- construir_tabla_algos(RESULTADOS_ALL, emp, ALGORITMOS_TODOS, ALGO_LABELS)

  if (is.null(resultado)) {
    cat(paste0("\n\n### Table ", tabla_num, ": ", emp, " - no data\n\n"))
    next
  }

  n_algos <- length(resultado$algos_usados)

  tbl <- kbl(resultado$tabla,
      format = fmt,
      caption = paste0("Algorithm comparison -- ", emp,
                       " (Model M3: ΔS± AH/PM)"),
      col.names = c("", colnames(resultado$tabla)[-1]),
      align = c("l", rep("c", n_algos)),
      booktabs = TRUE,
      linesep = "",
      escape = FALSE)

  if (es_pdf) {
    tbl <- tbl %>%
      kable_styling(
        latex_options = c("HOLD_position", "scale_down"),
        font_size = 8
      )
  } else {
    tbl <- tbl %>%
      kable_classic(full_width = FALSE, html_font = "Cambria", font_size = 13) %>%
      column_spec(1, width = "7em") %>%
      column_spec(2, border_left = TRUE)
    if (n_algos > 1) {
      for (col_i in 3:(n_algos + 1)) {
        tbl <- tbl %>% column_spec(col_i, border_left = "1px solid #ddd")
      }
    }
    for (br in resultado$sent_boundary_rows) {
      tbl <- tbl %>% row_spec(br, extra_css = "border-bottom: 1px solid #ddd;")
    }
  }

  tbl <- tbl %>%
    add_header_above(c(" " = 1, "Sentiment algorithm" = n_algos),
                     bold = TRUE, line = TRUE)

  for (g in resultado$pack_grupos) {
    tbl <- tbl %>%
      pack_rows(g$label, g$start, g$end,
                bold = TRUE, italic = FALSE,
                hline_before = TRUE, hline_after = FALSE,
                latex_gap_space = "0.3em")
  }

  tbl <- tbl %>%
    footnote(
      general = paste0("N = ", resultado$n_obs, " trading days.\\ ",
                       "*** p<0.001  ** p<0.01  * p<0.05  † p<0.1."),
      footnote_as_chunk = TRUE,
      threeparttable = es_pdf,
      escape = FALSE
    )

  print(tbl)
}
```

# =============================================================================
# PART F: EXPORT AND SUMMARY
# =============================================================================

```{r exportar_csv}
write.csv(RESULTADOS_ALL, file.path(DIR_OUTPUT, "comments_results.csv"), row.names = FALSE)
cat("CSV saved\n")
```

```{r guardar_helper_manuscrito}
helper_v4 <- list(
  RESULTADOS_ALL          = RESULTADOS_ALL,
  fmt_celda               = fmt_celda,
  nombre_var_display      = nombre_var_display,
  construir_tabla_descomp = construir_tabla_descomp,
  construir_tabla_algos   = construir_tabla_algos,
  ALGO_PRINCIPAL          = ALGO_PRINCIPAL,
  ALGO_LABELS             = ALGO_LABELS,
  TICKERS                 = TICKERS,
  MA_DIAS                 = MA_DIAS,
  ALGORITMOS_TODOS        = ALGORITMOS_TODOS,
  empresas_disponibles    = empresas_disponibles
)
saveRDS(helper_v4, file.path(DIR_OUTPUT, "helper_comments.rds"))
cat("helper_comments.rds saved in", DIR_OUTPUT, "\n")
```
